UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-16 paper/paper.tex
add distance alg

This metric represents distance from intersection points calculated based on uptime. Values can be negative to indicate non-optimal profile or positive otherwise. There are cases when it is better to be either below or above a threshold. It will be specified by flag parameter calculated together with \textit{ip(scheme1, scheme2)} results. Algorithm~\ref{alg:distance_from_optimality} represents pseudo code implementation.

\begin{algorithm}[H]
 \label{alg:distance_from_optimality}
 \KwData{Uptime, Intersection Point, Spin;}
 \KwResult{Distance from intersection point [-24, 24];}
  \If{Spin} {
        return Uptime - Intersection Point
  } 
  \Else{
        return Intersection Point - Uptime
  }
\caption{Uptime Based Distance From Intersection Points}
\end{algorithm}

Example algorithm results
\begin{enumerate}
\item Input: Uptime: 24, Optimality Point: 18, Spin: True (more optimal for values above threshold). Output: +6
\item Input: Uptime: 16, Optimality Point: 18, Spin: True (more optimal for values above threshold). Output: -2
\item Input: Uptime: 15, Optimality Point: 18, Spin: False (more optimal for values below threshold). Output: +3
\item Input: Uptime: 19, Optimality Point: 18, Spin: False (more optimal for values below threshold). Output: -1
\end{enumerate}

@@

 %  \ForAll{machine in Other Machines} {
%        \If{$machine.cpu \geq cluster.cpu$} {
%        \If{a}
 %              \State test % spare_cpu  cluster.cpu  machine.cpu
 %        \EndIf
%        \If{machine.memory < cluster.memory} {
%                spare_memory += cluster.memory - machine.memory
%        }
 %  }
\ForAll{machine in Other Machines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spare_cpu  clustercpu  machinecpu$
        }
        %\EndIf
}
%\EndFor
% \end{algorithmic}
\end{algorithm}

>>>>

This metric represents distance from intersection points calculated based on uptime. Result can be negative - indicates non-optimal profile - or positive otherwise. Positive and negative values can be yielded in either direction of time axis as presented on Figure~\ref{fig:distance}. 
It will be specified by flag parameter calculated together with \textit{ip(scheme1, scheme2)} results. Algorithm~\ref{alg:distance_from_optimality} represents pseudo code implementation.

\begin{figure}[H]
       \includegraphics[width=\linewidth]{figures/distance}
      \caption{Distance from intersection points. Positive (green) values indicate optimal result. Negative (red) represent data for further improvement.}
        \label{fig:distance}
\end{figure}

\begin{algorithm}[H]
 \label{alg:distance_from_optimality}
 \KwData{Uptime, Intersection Point, Bias;}
 \KwResult{Distance from intersection point [-24, 24];}
  \If{Bias} {
        return Uptime - Intersection Point
  } 
  \Else{
        return Intersection Point - Uptime
  }
\caption{Uptime Based Distance From Intersection Points}
\end{algorithm}

Example algorithm results
\begin{enumerate}
\item Input: Uptime: 24, Optimality Point: 18, Bias: True (more optimal for values above threshold). Output: +6
\item Input: Uptime: 16, Optimality Point: 18, Bias: True (more optimal for values above threshold). Output: -2
\item Input: Uptime: 15, Optimality Point: 18, Bias: False (more optimal for values below threshold). Output: +3
\item Input: Uptime: 19, Optimality Point: 18, Bias: False (more optimal for values below threshold). Output: -1
\end{enumerate}

@@

 %  \ForAll{machine in Other Machines} {
%        \If{$machine.cpu \geq cluster.cpu$} {
%        \If{a}
 %              \State test % spare_cpu  cluster.cpu  machine.cpu
 %        \EndIf
%        \If{machine.memory < cluster.memory} {
%                spare_memory += cluster.memory - machine.memory
%        }
 %  }
\ForAll{machine in otherMachines}{
        \If{$machine.cpu < cluster.cpu$} {
                 $spareCpu += clusterCpu - machineCpu$
        }
        \If{$machine.memory < cluster.memory$}{
        	$spareMemory += clusterMemory - machineMemory$
        }
        %\EndIf
}
%\EndFor
% \end{algorithmic}
\end{algorithm}
